A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2023-06-27 pilot-publication/lab-book.Rmd
Start adding encryption

@@

## Write codebook to file
saveRDS(codebook, file = "data/codebook.rds")

>>>>

## Encrypt synthetic data before writing to file
encrypted.synth.data <-

@@

## Write codebook to file, but first remove the settings entry
codebook$settings <- NULL
saveRDS(codebook, file = "data/codebook.rds")
```

To develop locally both the data and the codebook need to be loaded.

```{r load-data}
data <- readRDS("data/synth-data.rds")
codebook <- readRDS("data/codebook.rds")
